COVID-19 Policy-Compliance in Europe

### 2020-12-25 Draft.Rmd
Added Latex version of regression formula and new plot showing predicted values for policy compliance in different european countries

---
title: "COVID-19 Policy-Compliance in Europe"
author: "Philipp Holz"
date: 'December 24, 2020'
output: pdf_document
bibliography: References.json

@@

It yields the following result. The continuous variables Stringency Index and Date are both statistically significant at the 0.05 level. They show that with increased stringency the mobility decreases, while a later date is associated with an increased mobility. Also all expressions of the categorical variable Country are significant at the 0.05 level, with the exception of the United Kingdom.

```{r Regression Table, echo=FALSE, results="asis", fig.align='center'}

@@

The United Kingdom being a non-significant exception in the non-hierarchical linear model is an interesting case, as we could observe from our previous diagram with the compliance-approximation that, on a country-level with a random intercept and a random slope, the linear regression line fitted the United Kingdom data exceptionally *well*. Thus, we require

THIS TABLE WILL BE UPDATED BEFORE FINAL SUBMISSION

| Variable                  | Coefficient | Std. Error | p-value      |
| ------------------------- | ----------- | ---------- | ------------ |
| Stringency Index          | -7.045e-01  | 9.107e-03  | < 2e-16 ***  |
| Date                      | 6.122e-02   | 1.993e-03  | < 2e-16 ***  |
| Belgium                   | 2.463e+00   | 8.466e-01  | 0.003649 **  |
| Denmark                   | 1.066e+01   | 8.430e-01  | < 2e-16 ***  |
| France                    | 5.306e+00   | 8.474e-01  | 4.25e-10 *** |
| Germany                   | 1.208e+01   | 8.445e-01  | < 2e-16 ***  |
| Ireland                   | 2.999e+00   | 8.523e-01  | 0.000439 *** |
| Italy                     | 5.026e+00   | 8.544e-01  | 4.39e-09 *** |
| Netherlands               | 5.089e+00   | 8.564e-01  | 3.09e-09 *** |
| Poland                    | 7.011e+00   | 8.443e-01  | < 2e-16 ***  |
| Spain                     | 2.109e+00   | 8.523e-01  | 0.013401 *   |
| Sweden                    | 1.117e+01   | 8.431e-01  | < 2e-16 ***  |
| United Kingdom            | -2.997e-01  | 8.499e-01  | 0.724393     |

>>>>

---
title: "COVID-19 Policy-Compliance in Europe"
author: "Philipp Holz"
date: 'December 24, 2020'
output: 
  pdf_document:
    toc: true
    latex_engine: xelatex
bibliography: References.json

@@

\begin{equation}
{Compliance Index} = {\beta}_0 + {\beta}_1 * {Date} + {\beta}_2 * {Country} + {\beta}_3 * {Publicity} + {\beta}_4 * {Cases/100.000/14 days} + {\epsilon}
\end{equation}

It yields the following result. Except for Date, non of the continuous variables Publicity and Cases/100.000/14 Days are statistically significant. Date is statistically significant at the 0.05 level. It's coefficient shows that when holding Publicity, Cases and Country constant, Compliance decreases by 0.07 points each day.

With Country as the categorical variable, all expressions are statistically significant at the 0.05 level, with the exception of Belgium, Ireland, the Netherlands and the United Kingdom, when compared to Austria as the reference category. The adjusted R² indicates that the model explains 29% of the observed variance.

```{r Regression Table, echo=FALSE, fig.align='center', results="asis"}

@@

## Linear Multi-Level Model

However, when plotting the fitted values from the non-hierarchical linear model by country, we can observe different discrete levels of compliance by date, e.g. with Austria showing much higher levels of compliance than Germany and Sweden.

```{r Linear model predictions by country, echo=FALSE, fig.align='center', message=FALSE, warning=FALSE}
### Visualising different predicted intercepts and different slopes
ggplot(data = augment(lm(data = data, 
                         ComplianceIndex ~ Date + CountryName + Publicity + notification_rate_per_100000_population_14.days)),
       aes(x = Date, y = ComplianceIndex, color = CountryName))  +
  geom_smooth(aes(y = .fitted), method = "lm", se = FALSE) +
  xlab("Month") +
  scale_x_date(breaks = date_breaks("3 months"),
               labels = date_format("%b\n%Y")) +
  scale_y_continuous(name = "Policy Compliance Index") +
  theme(
    axis.title.y = element_text(color = "black", size=12, vjust = 3),
    axis.title.x = element_text(size=12, vjust = 0.5)
    ) +
  ggtitle("Model Predictions for Policy Compliance in Europe Across Time")
```

This suggests creating a hierarchical model with a random intercept for country in order to improve model fit.
